A molecular dynamics study of the solvation of carbon dioxide and other compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}

### 2019-02-12 ionic_liquids.tex
add figures of eq pressure

One can see in Table \ref{table:henry} that the only model able to reproduce the experimental Henry's law constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} with small deviation is that of Koller \textit{et al}. \cite{Koller_2012}.
The worst results are obtained with the models of Batista \textit{et al}. \cite{Batista_2015} and Liu \textit{et al}. \cite{Liu_2014}.
These models fail in part because of the small values they predict for $\Delta G_\text{vdW}$.
In order to analyze the model distinctions in more detail, in Fig.~\ref{fig:deltag} we plot free energy profiles with respect to the coupling parameter $\lambda_\text{vdW}$, as obtained from the simulations with all \ce{[emim][B(CN)_4]} models.
We observe that the model of Batista \textit{et al}. \cite{Batista_2015} is the one that predicts the smallest free-energy barrier, immediately followed by the model of Liu \textit{et al}. \cite{Liu_2014}.
This observation suggests that these models underestimate the magnitude of the solvent-solvent interactions, thus making it easier to open a cavity in the system for inserting the solute.
Besides, it also explains why these models underestimate the density of \ce{[emim][B(CN)_4]}, such as seen in Table~\ref{table:props_dsf}.
The Liu \textit{et al}. \cite{Liu_2014} model predicts the smallest value of $\Delta G_\text{vdW}$ in spite of exhibiting only the second smallest free-energy barrier.
This occurs because the attractive van der Waals interactions compensate the cavity formation more favorably than in the case of Batista \textit{et al}. \cite{Batista_2015}, as one can observe in Fig.~\ref{fig:deltag} as $\lambda_\text{vdW}$ approaches unity.
Nevertheless, these distinctions end up being canceled out when the charges of the \ce{CO_2} molecule are introduced, since $\Delta G_\text{vdW}$ and $\Delta G_\text{Coul}$ sum up to very similar $\Delta G_\text{sim}$ results for both models.

@@

One of the goals of this paper was to compare various available molecular models of \ce{[emim][B(CN)_4]} in terms of their capabilities to reproduce the experimental Henry's law constant of \ce{CO_2}.
We have found that only the force field developed by Koller \textit{et al}. \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8\%.
A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in the original work, which also allows one to accurately reproduce the experimental density of the pure substance.

We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}, we concluded that the Damped-Shifted-Force method for electrostatic interactions, with a damping factor $\alpha = 0.2 ~\text{\AA}^{-1}$, is a suitable strategy.
Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
Besides the properties already mentioned, the different models showed quite distinct behaviors, as well, in terms of conformational statistics.
%This lack of consistency is one of the reasons why in industry molecular simulation has not become a routinely tool yet.

The solvation free energy results at infinite-dilution condition suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}, despite the similarity in the Henry's law constants observed in both cases.
This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][Tf_2N]} in an equal-mass basis.

>>>>

Table \ref{table:henry} shows that the only model able to reproduce the experimental Henry's law constant of \ce{CO_2} in \ce{[emim][B(CN)_4]} with small deviation is that of Koller \textit{et al}. \cite{Koller_2012}.
The worst results are obtained with the models of Batista \textit{et al}. \cite{Batista_2015} and Liu \textit{et al}. \cite{Liu_2014}.
These models fail in part because of the small values they predict for $\Delta G_\text{vdW}$.
In order to analyze the model distinctions in more detail, in Fig.~\ref{fig:deltag} we plot free energy profiles with respect to the coupling parameter $\lambda_\text{vdW}$, as obtained from the simulations with all \ce{[emim][B(CN)_4]} models.
We observe that the model of Batista \textit{et al}. \cite{Batista_2015} is the one that predicts the smallest free-energy barrier, immediately followed by the model of Liu \textit{et al}. \cite{Liu_2014}.
This observation suggests that these models underestimate the magnitude of the solvent-solvent interactions, thus making it easier to open a cavity in the system for inserting the solute.
Besides, it also explains why these models underestimate the density of \ce{[emim][B(CN)_4]}, such as seen in Table~\ref{table:props_dsf}.
The Liu \textit{et al}. \cite{Liu_2014} model predicts the smallest value of $\Delta G_\text{vdW}$ in spite of exhibiting only the second smallest free-energy barrier.
This occurs because the attractive van der Waals interactions compensate the cavity formation more favorably than in the case of Batista \textit{et al}. \cite{Batista_2015}, as one can observe in Fig.~\ref{fig:deltag} as $\lambda_\text{vdW}$ approaches unity.
Nevertheless, these distinctions end up being canceled out when the charges of the \ce{CO_2} molecule are introduced, since $\Delta G_\text{vdW}$ and $\Delta G_\text{Coul}$ sum up to very similar $\Delta G_\text{sim}$ results for both models.

@@

One of the goals of this paper was to compare various available molecular models of \ce{[emim][B(CN)_4]} in terms of their capabilities to reproduce the experimental Henry's law constant of \ce{CO_2}.
We have found that only the force field developed by Koller \textit{et al}. \cite{Koller_2012} is able to perform such task, with a small relative error of 2.8\%.
A key factor for its success seems to be the reparametrization of the LJ parameters for the boron atom carried out in the original work, which also allows to accurately reproduce the experimental density of the pure substance.

We focused also on exploring alternative simulation strategies with the goal of gaining computational efficiency.
Particularly, for both \ce{[emim][B(CN)_4]} and \ce{[emim][Tf_2N]}, we concluded that the Damped-Shifted-Force method for electrostatic interactions, with a damping factor $\alpha = 0.2 ~\text{\AA}^{-1}$, is a suitable strategy.
Other improvement was the use of rigid bodies to simulate \ce{[emim][B(CN)_4]}.
This required preliminary simulations in order to examine the flexibility of the ethyl chain in \ce{[emim]^+} and the analysis was greatly facilitated by employing useful visualization tools.
Besides the properties already mentioned, the different models showed quite distinct behaviors in terms of conformational statistics.
%This lack of consistency is one of the reasons why in industry molecular simulation has not become a routinely tool yet.

The solvation free energy results suggest that a more favorable solvation of \ce{CO_2} occurs in \ce{[emim][B(CN)_4]} than in \ce{[emim][Tf_2N]}, despite the similarity in the Henry's law constants observed in both cases.
This picture is further confirmed at high \ce{CO_2} concentrations, in which the simulations correctly predicted that a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}, as compared to \ce{[emim][Tf_2N]} in an equal-mass basis.
